### 2016-12-07 paper/chapters/gan.tex
added (short) BN, DCGAN and LAPGAN texts

@@

\subsection{Application}
\label{sub:gan_application}
GAN have been applied to many different areas which include generating images (GAN, DCGAN, LAPGAN), sequences (SeqGAN), videos (\cite{gan_video:2016}), 3D objects (\cite{gan_3d:2016}), text-to-image synthesis (\cite{gan_t2i:2016})
\subsection{Extensions}
\label{sub:gan_extensions}

\subsubsection{LAPGAN}
\label{ssub:lapgan}

\subsubsection{DCGAN}
\label{ssub:dcgan}

>>>>

\subsubsection{(Virtual) Batch normalization}
\label{ssub:gan_batch_norm}
Using batch normalization \cite{batch_norm:2015} helped stabilizing learning DCGAN \cite{dcgan:2015}.
\cite{improved_gan:2016} introduced virtual batch normalization where each input $x$ is normalized on one reference batch chosen at the start of learning instead of the other inputs in the mini-batch.

@@

\subsection{Application}
\label{sub:gan_application}
GAN have been applied to many different areas which include generating images (GAN, DCGAN, LAPGAN), sequences (SeqGAN), videos (\cite{gan_video:2016}), 3D objects (\cite{gan_3d:2016}), text-to-image synthesis (\cite{gan_t2i:2016})

\subsection{Extensions}
\label{sub:gan_extensions}

\subsubsection{DCGAN \cite{dcgan:2015}}
\label{ssub:dcgan}
Early implementations of the GAN framework have been implemented using fully-connected layers,
which have proven to be difficult and slow to train on real-world data (citation, original convnet papers?).
Using deep convolutional networks has helped reach human-level performance in object recognition and classification problems on images (citations!).
As the discriminator in the GAN model implements a binary classification task and the generator performance is heavily dependent on the discriminator, using convnets to train the model should improve performance of image generation immensely.
\emph{Deep convolutional generative adversarial network} (DCGAN) has applied convolutional networks to both generator and discriminator, resulting in quantitively evualuated better results.
DCGAN uses no fully connected or pooling layers, but instead fractionally strided convolutions (often wrongfully called deconvolutions).

\subsubsection{LAPGAN \cite{lapgan:2015}}
\label{ssub:lapgan}
LAPGAN is an extension of GAN applied to images using laplacian pyramids \cite{laplacian:1983}.
Instead of using a single generator network, LAPGAN uses a series of deep convolutional networks as generators.

\paragraph{Training} is heavily modified from the regular GAN framework.
In each iteration a training sample is drawn from the dataset and a downsamples version from it is computed.
The discriminator receives now either the computed high-pass image (from the original image and the down-then-up sampled image) or an high-pass image from the generator.
These steps are repeated for other steps, downscaling the image.
In the last stage, a traditional generator and discriminator is used for the $8x8$ image.
\paragraph{Sampling} uses a conditional GAN to produce high-resolution images through different stages of deep generator networks.

\paragraph{Results}
As GANs have no direct measurement of the quality of generations due to their lack of objective function, human evaluation of the authenticity of generated images is used for quantitive results.
LAPGAN has pushed the state of the art significantly, with generated images which are high-resolution in comparison to earlier methods and arguebly high variety of generations.
Furthermore, humans have evaluated the generated images for real images 40\% of the time.
